\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-11-17 doc/paper.tex
fix typo.
added instrcutions for editing FlexibleSUSY.m to make it useful for the NMSSM.

{{ Description -> "Singlet-VEV", 
			 LaTeX -> "v_s",
             Value -> None, 
             LesHouches -> {NMSSMRUN,5},
             OutputName-> vS         }},
\end{lstlisting}
\item Navigate to Flexible SUSY directory  \code{cd /path/to/FlexibleSUSY/}
\item Create Z3NMSSM directory 
\begin{lstlisting}
./createmodel --models=Z3NMSSM:myNMSSM
\end{lstlisting}

@@

\item Add Singlet Higgs superfield to SuperFields
\begin{lstlisting}
SuperFields[[8]] = {s, 1, sR,     0, 1,  1, Qs, RpP};
\end{lstlisting}\end{lstlisting}
\item Add inert Higgs-like superfields 
\begin{lstlisting}
SuperFields[[9]] = {H1I, 2, {H1I0, H1Im},  -1/2, 2, 1, QHu, RpP};
SuperFields[[10]] = {H2I, 2, {H2Ip, H2I0},   1/2, 2, 1, QHd, RpP};
SuperFields[[11]] = {sI, 2, sR,    0, 1,  1, Qs, RpM};
\end{lstlisting}
\item Add exotics to SuperFields
\begin{lstlisting}
SuperFields[[12]] = {Dx, 3, conj[DxR],  1/3, 1, -3, QDx, RpP};
SuperFields[[13]] = {Dxbar, 3, conj[DxbarR],  -1/3, 1, 3, QDxbar, RpP};
\end{lstlisting}
\item Add additional survival $SU(2)$ multiplets to SuperFields
\begin{lstlisting}
SuperFields[[14]] = {Hp, 1, conj[HpR],    0.5, 2,  1, QHp, RpP};
SuperFields[[15]] = {Hpbar, 1, conj[HpbarR],    -0.5, 2,  1, QHpbar, RpP};
\end{lstlisting}
\item Modify superpotential
\begin{lstlisting}
SuperPotential = Yu u.q.Hu - Yd d.q.Hd - Ye e.l.Hd + \[Lambda] S.Hu.Hd +  La S.H2I.H1I + \[Kappa] S.Dx.Dxbar;
\end{lstlisting}
\item Add new VEV
\begin{lstlisting} DEFINITION[EWSB][VEVs]= 
  { {SHd0, {vd, 1/Sqrt[2]}, {sigmad, \[ImaginaryI]/Sqrt[2]},{phid,1/Sqrt[2]}},
    {SHu0, {vu, 1/Sqrt[2]}, {sigmau, \[ImaginaryI]/Sqrt[2]},{phiu,1/Sqrt[2]}},
    {SsR,  {vs, 1/Sqrt[2]}, {sigmaS, \[ImaginaryI]/Sqrt[2]},{phiS,1/Sqrt[2]}}
};
\end{lstlisting}

@@

\end{thebibliography}
\end{document}

>>>>

{{ Description -> "Singlet-VEV", 
			 LaTeX -> "v_s",
             Value -> None, 
             LesHouches -> {NMSSMRUN,5},
             OutputName-> vS         }},
\end{lstlisting}
\item Navigate to Flexible SUSY directory  \code{cd /path/to/FlexibleSUSY/}
\item Create Z3NMSSM directory \code{./createmodel --models=Z3NMSSM:myNMSSM}
\item Configure with the new model \code{./configure --with-models=Z3NMSSM}
\item The default FlexibleSUSY model file for the MSSM will now be in the models/NMSSM2 directory.  Edit this for the NMSSM as follows:
  \begin{enumerate} 
    \item Add new input parameter $\lambda$.
      \begin{lstlisting}
        EXTPAR = { {61, LambdaInput} };
      \end{lstlisting}
     \item Also add this parameter to the DefaultParameterPoint.
      \begin{lstlisting}
       DefaultParameterPoint = {
    {m0, 125},
    {m12, 500},
    {TanBeta, 10},
    {Sign[\[Mu]], 1},
    {Azero, 0}
    {LambdaInput, 0.1}
    };
  \end{lstlisting}
    \item Name the parameters you wish to be output by the EWSB conditions.  Note you should use the names given for them in parameters.m.    A common choice in the NMSSM is:
\begin{lstlisting}
EWSBOutputParameters = {vS, \[Kappa], ms2};
\end{lstlisting}
which will work for the semi-constrained NMSSM.
\item choose the Highscale and Highscale first guess, if the default is different from what you wish to use.  
\begin{lstlisting} 
 HighScale = g1 == g2;
 HighScaleFirstGuess = 1.0 10^16;
\end{lstlisting}
\item Add how the parameters found in parameters.m that are to be set at the highscale:
\begin{lstlisting} 
HighScaleInput={
   {T[Ye], Azero*Ye},
   {T[Yd], Azero*Yd},
   {T[Yu], Azero*Yu},
   {mHd2, m0^2},
   {mHu2, m0^2},
   {mq2, UNITMATRIX[3] m0^2},
   {ml2, UNITMATRIX[3] m0^2},
   {md2, UNITMATRIX[3] m0^2},
   {mu2, UNITMATRIX[3] m0^2},
   {me2, UNITMATRIX[3] m0^2},
   {MassB, m12},
   {MassWB,m12},
   {MassG,m12},
{\[Lambda], LambdaInput},
   {T[\[Kappa]], Azero \[Kappa]},
   {T[\[Lambda]], Azero LambdaInput}
};
\end{lstlisting}
\item set lowscale boundary condititions if you want something different from the default.  The defaults are:
\begin{lstlisting} 
 LowScale = SM[MZ];
 LowScaleFirstGuess = SM[MZ];
\end{lstlisting}
\item Change the LowscaleInput if necessary.  In this example we keep the same choice as in the MSSM
  \begin{lstlisting} 
 LowScaleInput={
   {vd, 2 MZDRbar / Sqrt[GUTNormalization[g1]^2 g1^2 + g2^2] Cos[ArcTan[TanBeta]]},
   {vu, 2 MZDRbar / Sqrt[GUTNormalization[g1]^2 g1^2 + g2^2] Sin[ArcTan[TanBeta]]}
};
  \end{lstlisting}

Finally we set the initial guesses for the paremeters.  In this example we overwtite the MSSM version replacing it with:
 \begin{lstlisting} 
InitialGuessAtLowScale = {
   {vd, SM[vev] Cos[ArcTan[TanBeta]]},
   {vu, SM[vev] Sin[ArcTan[TanBeta]]},
   {\[Lambda], LambdaInput},
   {\[Kappa], 0.1},
   {vS, 1000},
   {ms2, SM[MZ]^2}
};

InitialGuessAtHighScale = {};
 \end{lstlisting}

The code can now be created and also compiled (if you didn't select --disable-compile option when you ran the configure script) by typing \code{make -j2}.

@@

\item Add Singlet Higgs superfield to SuperFields
\begin{lstlisting}
SuperFields[[8]] = {s, 1, sR,     0, 1,  1, Qs, RpP};
\end{lstlisting}
\item Add inert Higgs-like superfields 
\begin{lstlisting}
SuperFields[[9]] = {H1I, 2, {H1I0, H1Im},  -1/2, 2, 1, QHu, RpP};
SuperFields[[10]] = {H2I, 2, {H2Ip, H2I0},   1/2, 2, 1, QHd, RpP};
SuperFields[[11]] = {sI, 2, sR,    0, 1,  1, Qs, RpM};
\end{lstlisting}
\item Add exotics to SuperFields
\begin{lstlisting}
SuperFields[[12]] = {Dx, 3, conj[DxR],  1/3, 1, -3, QDx, RpP};
SuperFields[[13]] = {Dxbar, 3, conj[DxbarR],  -1/3, 1, 3, QDxbar, RpP};
\end{lstlisting}
\item Add additional survival $SU(2)$ multiplets to SuperFields
\begin{lstlisting}
SuperFields[[14]] = {Hp, 1, conj[HpR],    0.5, 2,  1, QHp, RpP};
SuperFields[[15]] = {Hpbar, 1, conj[HpbarR],    -0.5, 2,  1, QHpbar, RpP};
\end{lstlisting}
\item Modify superpotential
\begin{lstlisting}
SuperPotential = Yu u.q.Hu - Yd d.q.Hd - Ye e.l.Hd + \[Lambda] S.Hu.Hd +  La S.H2I.H1I + \[Kappa] S.Dx.Dxbar;
\end{lstlisting}
\item Add new VEV
\begin{lstlisting} DEFINITION[EWSB][VEVs]= 
  { {SHd0, {vd, 1/Sqrt[2]}, {sigmad, \[ImaginaryI]/Sqrt[2]},{phid,1/Sqrt[2]}},
    {SHu0, {vu, 1/Sqrt[2]}, {sigmau, \[ImaginaryI]/Sqrt[2]},{phiu,1/Sqrt[2]}},
    {SsR,  {vs, 1/Sqrt[2]}, {sigmaS, \[ImaginaryI]/Sqrt[2]},{phiS,1/Sqrt[2]}}
};
\end{lstlisting}

@@

\end{thebibliography}
\end{document
}
